Response to Reviews

### 2025-07-15 paper/review1/ReponseToReviewers2025.qmd
done with all - needs a careful read and references cleaned up
added code file and checked response

---
title: "Response to Reviewers"
format: pdf
editor: visual
---

## Response to Editor and reviewers

Thank you for the careful reviews of our paper. Please find *our responses to provided in italics* point-by-point with the comments.

@@

*XXX*

@@

*Done*

@@

*The explanation of data cleaning has been revised to make it clearer. There is no difference in XXX*

@@

*There is no difference in results from group A and B. XXX*

>>>>

---
title: "Response to Reviews"
author: "Stephanie Kobakian and Dianne Cook"
format: pdf
editor: visual
---

Thank you for the careful reviews of our paper. Please find *our responses provided point-by-point with the comments in italics*.

@@

@@

@@

*The explanation of data cleaning has been revised to make it clearer. There is no difference in in groups or participant demographics. This is written in the text now bu results not included. The code for these checks is in the unevaluated chunks the qmd file.*

@@

*There is no difference in results from group A and B. There is no difference in in groups or participant demographics. This is written in the text now bu results not included. The code for these checks is in the unevaluated chunks the qmd file.*
